---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE)
```

```{r load packages, echo = FALSE, include = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)
library(patchwork)
```

```{r Set variables, echo = FALSE}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
#raw_repo <- '2023_Liege_BLAM_MB_raw'
# January update: logs from session 02, 03 and 04 are not in raw GIN repo yet so this is a backup manual fusion with OneDrive logs
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script

#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)


#This is the WIDTH of the time window for accuracy, i.e. responses will be bound to targets if they occurr within that TW
accu_tw <- 3
#env cleanup
rm(raw_repo)

## Source the functions 
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))
```

```{r Audio Localizer: Data Wrangling, echo = FALSE}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
#sub_EB <- c('01','03','04', '05','06','07')
#sub_SC <- c('02','03','04', '05','06', '07')

## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER

#SEPTEMBER SUBJECTS
#sub_SC <- c('01','02','03','04', '06', '07')
#sub_EB<- c('01','02','03','04', '05','07')

#JANUARY SUBJECTS 
# EB02 DIDM'T RESPOND!
sub_SC <- c('01','02','03','04', '06', '07', '08', '09', '10', '11', '12', '13', '14')
sub_EB<- c('01','03','04','06', '05','07', '08', '09', '10', '11')
task <- 'auditoryLocalizer'
conditions <- c('motion','static')
groups <- c('EB', 'SC')

# Prepare an empty df 
df_AudioLoc_accu_cond <- data.frame(stringsAsFactors = FALSE)


#Loop across subjects 
for(g in seq_along((groups))){
    #for(i in seq_along(sub_SC)) {
    
    #depending on the group, pick the correct subjects list to loop across
    #I'm pretty sure this can be done more elegantly
    if(groups[g]=='EB'){
        curr_subs <- sub_EB
    }else if(groups[g] == 'SC'){
        curr_subs <- sub_SC
    }
    
    #loop across subjects
    for(i in seq_along(curr_subs)) {
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task
        # get rid of what looks like field map events?
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                  task, '.*',
                                                  "_events\\.tsv$"),
                                 recursive = TRUE) %>%
            #Drop the mag and phase events from the list
            str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
            str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
        
        

            temp_data<-read.table(paste(inputs, bids_sub, sub_events[1],
                                        sep = '/'), header=TRUE)
            
            
            for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pic given condition! 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #drop first event which is always flagged as a target?
                   # slice(-1) %>% 
                    mutate(soundTarget = recode(soundTarget, 'n/a' = '0')) %>% 
                    mutate(soundTarget = as.numeric(soundTarget)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = soundTarget)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                        cond = conditions[c],
                                        task = task, 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_AudioLoc_accu_cond <- rbind(df_AudioLoc_accu_cond, accu_temp)
                
            }
        
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_AudioLoc <- df_AudioLoc_accu_cond %>% 
    #filterout outliers :) 
    filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    group_by(group, cond) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )
```

```{r Audio localizer: Fix Targets Data Wrangling, echo = FALSE}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))



## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER

sub_SC <- c('01','02','03','04', '06', '07', '08', '09', '10', '11', '12', '13', '14')
groups <- c('SC')
task <- 'auditoryLocalizer'
#conditions <- c('motion','static')

# Prepare an empty df 
df_AudioLoc_accu_FIX <- data.frame(stringsAsFactors = FALSE)


#Loop across subjects 
for(g in seq_along((groups))){
    for(i in seq_along(sub_SC)) {
        
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task
        # get rid of what looks like field map events?
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                  task, '.*',
                                                  "_events\\.tsv$"),
                                 recursive = TRUE) %>%
            str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
            str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
        

            temp_data<-read.table(paste(inputs, bids_sub, sub_events[1],
                                        sep = '/'), header=TRUE)
            
            
            #for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pic given condition! 
                   # filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #drop first event which is always flagged as a target?
                   # slice(-1) %>% 
                    mutate(fixationTarget = recode(fixationTarget, 'n/a' = '0')) %>% 
                    mutate(fixationTarget = as.numeric(fixationTarget)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = fixationTarget)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                       # cond = conditions[c],
                                        task = task, 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_AudioLoc_accu_FIX <- rbind(df_AudioLoc_accu_FIX, accu_temp)
                
         #   }
        
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_AudioLoc_FIX <- df_AudioLoc_accu_FIX %>% 
    #filterout outliers :) 
    #filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    #group_by(group, cond) %>% 
    group_by(group) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )
```

```{r Visual Localizers: data wrangling, echo = FALSE}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
#sub_EB <- c('01','03','04', '05','06','07')
#sub_SC <- c('02','03','04', '05','06', '07')

## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER



# WHERE ARE THE EVENT FILES FROM sub-SC04?!
sub_SC <- c('01','02','03','04', '05','06', '07', '08', '09', '10', '11', '12', '13', '14')

task <- c('visualLocalizer','mtMstLocalizer')
# Prepare an empty df 
df_VisualLoc_accu <- data.frame(stringsAsFactors = FALSE)

groups <- 'SC'

#Loop across subjects 
for(g in seq_along((groups))){
    for(i in seq_along(sub_SC)) {
        
        
        bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        
        for(t in seq_along(task)){
            
            if(task[t] == 'visualLocalizer'){
                conditions = c('motion', 'static')
            }else if(task[t] == 'mtMstLocalizer'){
                conditions = 'motion'
            }
            
            #Grab events from this sub in this task
            # get rid of what looks like field map events?
            sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                     pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                      task[t], '.*',
                                                      "_events\\.tsv$"),
                                     recursive = TRUE) %>%
                str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
                str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
            
            
            for(j in seq_along(sub_events)){
                
                temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                            sep = '/'), header=TRUE)
                
                
                for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pick given condition! 
                    filter((!grepl('trigger', trial_type))) %>% 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #drop first event which is always flagged as a target?
                    # slice(-1) %>% 
                    mutate(target = recode(target, 'n/a' = '0')) %>% 
                    mutate(target = as.numeric(target)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = target)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                        cond = conditions[c],
                                        task = task[t], 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_VisualLoc_accu <- rbind(df_VisualLoc_accu, accu_temp)
                
                }
            }
        }
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_VisualLoc <- df_VisualLoc_accu %>% 
    #filterout outliers :) 
    #filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    group_by(task, cond) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )


```

```{r ANOVAS, echo = FALSE}
library(ez)
ANOVA_AudioLoc <- ezANOVA(
    data = df_AudioLoc_accu_cond, 
    dv = accu_percent,
    wid = subject,
    within = cond,
    between = group
)

ANOVA_VisLoc <-  df_VisualLoc_accu %>% 
    filter(task == 'visualLocalizer') %>% 
    ezANOVA(
    data = ., 
    dv = accu_percent, 
    wid = subject, 
    within = .(cond)
)
```

```{r Plots, echo = FALSE}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

labels_aud <- c('Motion (A)', 'Static (A)')

labels_vis <- c('Motion (V)', 'Static (V)')

## DFs: remove outliers! 
df_AudioLoc_accu_cond_blind <- df_AudioLoc_accu_cond %>% 
    filter(group == 'EB' & subject != 'sub-EB02')
df_AudioLoc_accu_cond_sighted <- df_AudioLoc_accu_cond %>% 
    filter(group == 'SC' & subject != 'sub-SC01')


df_VisualLoc_accu_plot <- df_VisualLoc_accu %>% 
    filter(task == 'visualLocalizer')

df_MT_MST_accu_plot <- df_VisualLoc_accu %>% 
    filter(task == 'mtMstLocalizer') 

## PLOT AUDIO 
plot_Audio_blind <- blam_accuracy_points_sum_conditions_group(df_AudioLoc_accu_cond_blind, 
                                                              labels_aud, 
                                                              dark_colors[1]) +
    scale_y_continuous(name = 'Accuracy [%]', 
                       limits = c(35,100))+ 
    ggtitle(label = 'Blind')

plot_Audio_sig <- blam_accuracy_points_sum_conditions_group(df_AudioLoc_accu_cond_sighted, 
                                                              labels_aud, 
                                                              dark_colors[2])+
    scale_y_continuous(name = 'Accuracy [%]', 
                       limits = c(35,100)) + 
    ggtitle(label = 'Sighted')

plot_AudioLoc <- plot_Audio_blind  + plot_Audio_sig

#BONUS: PLOT AUDIO FOR FIX TARGETS COLOR CHANGES IN SIGHTED
plot_Audio_fix_sig <- blam_accuracy_points_sum_group(df_AudioLoc_accu_FIX, dark_colors[2])

#rm(plot_Audio_blind, plot_Audio_sig)

## PLOT VISUAL 
plot_VisualLoc <- blam_accuracy_points_sum_conditions_group(df_VisualLoc_accu_plot, 
                                                              labels_vis, 
                                                              dark_colors[2])

plot_MT_MSTLoc <- blam_accuracy_points_sum_conditions_group(df_MT_MST_accu_plot, 
                                                              labels_vis, 
                                                              dark_colors[2])
```

```{r Plots: flag outliers with labels, echo = FALSE}

#Audio localizer labels: SC03 + SC06
plot_AudioLoc_outliers <- plot_Audio_blind  + (plot_Audio_sig +
                                                   annotate("text", 
                                                            x = 'motion', 
                                                            y = 41, 
                                                            label = 'sub-SC06') +
                                                   annotate("text", 
                                                            x = 'motion', 
                                                            y = 70, 
                                                            label = 'sub-SC03')) 

#Visual localizer: sub-SC06
plot_MT_MSTLoc_outliers <- plot_MT_MSTLoc + 
    annotate("text", 
             x = 'motion',
             y = 42, 
             label = 'sub-SC06') +
    ggtitle(label = 'MT/MST Localizer')

plot_VisualLoc_outliers <- plot_VisualLoc +
        annotate("text", 
             x = 'static',
             y = 65, 
             label = 'sub-SC06') +
    ggtitle(label = 'Visual Motion Localizer')
```

#BLAM 7T Behavioural analyses: Localizers

## Subjects:
11 Congenitally Blind 
13 Sighted Controls
(Some are excluded from analyses in certain tasks due to lack of responses)

## List of tasks: 
### Auditory Motion Localizer
Stimuli:

Experimental design:

Conditions & Task(s)

- *Motion* (**Press the button for repetition of sound direction**)
- *Static* (**Press the button for repeated double short bursts**)

Subject exclusions
sub-SC05 (data not acquired)
sub-EB02 (no responses)

### Visual Motion Localizer
Stimuli:

Experimental design:

Conditions & Task(s)

- *Motion* (**Press the button for repetition of sound direction**)
- *Static* (**Press the button for repeated double short bursts**)

Subject exclusions: 
sub-SC05 (data not acquired)


### MT/MST Localizer 
Stimuli:

Experimental design:

Conditions & Task(s)

- *Motion* (**Press the button for shorter event**)

Subject exclusions: 
sub-SC05 (data not acquired)


## Analytical approach:
Given no 1-to-1 matching between target events and responses the approach here
was to use the *time window* for correct answers, i.e., monitoring whether the 
response occurred within *3 seconds* of the target. 

Plots include individual values and group mean +- standard error. 

Group / conditions / axis of motion differences are tested with ANOVAs. 


## Auditory motion loc behavioural accuracy

Descriptive stats: group level [% correct]
```{r AudioLoc: descriptives}
df_group_AudioLoc
```

Plot (flagging outliers)
```{r AudioLoc: plot}
plot_AudioLoc_outliers
```

ANOVA 2 (group: blind + sighted) x 2 (condition: motion + static)
```{r AudioLoc: anova}
ANOVA_AudioLoc
```
While there are 2 sighted outliers with worse performance, there are no differences between blind and sighted and between motion and static conditions. 


## Visual Motion localizers (regular + MT/MST)
Descriptive stats: group level [% correct]
```{r VisLoc: descriptives}
df_group_VisualLoc
```

Plot (flagging outliers)

```{r VisLoc: plot}
plot_VisualLoc_outliers
```

```{r MT/MSTLoc: plot}
plot_MT_MSTLoc_outliers
```


ANOVA (Vis motion only, since there is no static condition in MT/MST localizer. Equvalent of a T test)
```{r VisLoc: anova}
ANOVA_VisLoc
```

sub SC-06 is performing worse, but there are no differences between conditions. 