---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

3.  Bimidal motion auditory
4.  Bimodal motion visual


Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)
library(patchwork)
library(ez)
```

## Define basic variables

```{r, echo = FALSE}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
#tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
#           'task-bimodalMotionAud', 'task-bimodalMotionVis')

accu_tw <- 3
#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')
#env cleanup
rm(raw_repo)
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))
```


## BIMODAL MOTION AUDIO - MOTION VS STATIC
Main analyses
```{r}
# This has to go by runs 

## FOR NOW THE SCRIPT CRASHES AS IT ASSUMES IDENTICAL NUMBER OF SUBJECTS PER GROUP
## THERE MUST BE A BETTER WAY TO DO IT, e.g. list of all subjects and then extracting the group from sub
#sub_SC <- c('01','02','03','04','07')
#sub_EB<- c('01','02','03', '06','05','07')

sub <- c('EB01','EB02','EB03', 'EB06','EB05','EB07',
         'SC01','SC02','SC03','SC04','SC07')

task <- 'bimodalMotionAud'
conditions <- c('auditory_motion', 'auditory_static')

#Prepare df to store group accuracy
df_BimodAudio_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)
df_BimodAudio_run_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
#for(g in seq_along(groups)){
   # for(i in seq_along(sub_EB)) {
        for(i in seq_along(sub)) {
        
        #Pick a subject from correct list 
       # if(groups[g]=='EB'){
        #    bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        #}else if(groups[g]=='SC'){
        #    bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        #}
        gr <- str_sub(sub[i],1,2)
        bids_sub <- paste0('sub-',sub[i])
        
        #Grab events from this sub in this task 
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                                 recursive = TRUE)
        
        sub_accu <- data.frame(stringsAsFactors = FALSE)
        
        
        
        for(j in seq_along(sub_events)){
            
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                        sep = '/'), header=TRUE)
            
            for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events
                    #filter((!grepl('trigger', trial_type))) %>% 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #mutate(target = as.numeric(target)) %>% 
                    #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
                    # 3 = static target / 2 = motion target? but only for sub 01 & 02
                    # rest have 2.000 as a general audio target
                    mutate(target = recode(target, 
                                           #Change all souund targets to 1
                                           '3' = '1', 
                                           '2' = '1',
                                           '2.000000' = '1',
                                           # Change all visual fix targets to 0!
                                           '1.000000' = '0',
                                           '1' = '0',
                                           'n/a' = '0')) %>% 
                    mutate(target_func = target)
                
                
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        #group = groups[g],
                                        group = gr,
                                        cond = conditions[c],
                                        run_num = j,
                                        run_lab = paste0('run-0',j),
                                        task = task, 
                                        accu_percent = accu_percent) %>% 
                     mutate(cond = factor(cond, levels = c('auditory_motion', 'auditory_static')))
                #Add this run to subject data
                sub_accu <- rbind(sub_accu, accu_temp)
                
                
                
            }
            
            #Add data to accuracies by RUN
            df_BimodAudio_run_accu_cond <- rbind(df_BimodAudio_run_accu_cond, sub_accu)
            
            
        }
        sub_accu_mean <- sub_accu %>% 
            group_by(cond) %>% 
            mutate(accu_percent = mean(accu_percent)) %>% 
            dplyr::select(-c(run_lab, run_num)) %>% 
            slice(1)
        
        #Add data to accuracy summaries by subject
        df_BimodAudio_summ_accu_cond<- rbind(df_BimodAudio_summ_accu_cond, sub_accu_mean)
    }
#}

    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)   
```

## BIMODAL MOTION AUDIO - CONDITION X AXIS

```{r}
# This has to go by runs 

## FOR NOW THE SCRIPT CRASHES AS IT ASSUMES IDENTICAL NUMBER OF SUBJECTS PER GROUP
## THERE MUST BE A BETTER WAY TO DO IT, e.g. list of all subjects and then extracting the group from sub
#sub_SC <- c('01','02','03','04','07')
#sub_EB<- c('01','02','03', '06','05','07')

sub <- c('EB01','EB02','EB03', 'EB06','EB05','EB07',
         'SC01','SC02','SC03','SC04','SC07')

task <- 'bimodalMotionAud'
conditions <- c('auditory_motion', 'auditory_static')
axis_list <- c('vertical', 'horizontal') 

#Prepare df to store group accuracy
df_BimodAudio_summ_accu_cond_axis <- data.frame(stringsAsFactors = FALSE)
df_BimodAudio_run_accu_cond_axis <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
#for(g in seq_along(groups)){
   # for(i in seq_along(sub_EB)) {
        for(i in seq_along(sub)) {
        
        #Pick a subject from correct list 
       # if(groups[g]=='EB'){
        #    bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        #}else if(groups[g]=='SC'){
        #    bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        #}
        gr <- str_sub(sub[i],1,2)
        bids_sub <- paste0('sub-',sub[i])
        
        #Grab events from this sub in this task 
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                                 recursive = TRUE)
        
        sub_accu <- data.frame(stringsAsFactors = FALSE)
        
        
        
        for(j in seq_along(sub_events)){
            
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                        sep = '/'), header=TRUE)
            
            for(c in seq_along(conditions)){
                
                for(a in seq_along(axis_list)){
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events
                    #filter((!grepl('trigger', trial_type))) %>% 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    filter(axis == axis_list[a] | axis == 'n/a') %>% 
                    #mutate(target = as.numeric(target)) %>% 
                    #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
                    # 3 = static target / 2 = motion target? but only for sub 01 & 02
                    # rest have 2.000 as a general audio target
                    mutate(target = recode(target, 
                                           #Change all souund targets to 1
                                           '3' = '1', 
                                           '2' = '1',
                                           '2.000000' = '1',
                                           # Change all visual fix targets to 0!
                                           '1.000000' = '0',
                                           '1' = '0',
                                           'n/a' = '0')) %>% 
                    mutate(target_func = target)
                
                
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        #group = groups[g],
                                        group = gr,
                                        cond = conditions[c],
                                        axis = axis_list[a],
                                        run_num = j,
                                        run_lab = paste0('run-0',j),
                                        task = task, 
                                        accu_percent = accu_percent) %>% 
                     mutate(cond = factor(cond, levels = c('auditory_motion', 'auditory_static')))
                #Add this run to subject data
                sub_accu <- rbind(sub_accu, accu_temp)
                
                
                
           
            
            #Add data to accuracies by RUN
            df_BimodAudio_run_accu_cond_axis <- rbind(df_BimodAudio_run_accu_cond_axis, sub_accu)
                }
            }
        }
        sub_accu_mean <- sub_accu %>% 
            group_by(cond, axis) %>% 
            mutate(accu_percent = mean(accu_percent)) %>% 
            dplyr::select(-c(run_lab, run_num)) %>% 
            slice(1)
        
        #Add data to accuracy summaries by subject
        df_BimodAudio_summ_accu_cond_axis<- rbind(df_BimodAudio_summ_accu_cond_axis, sub_accu_mean)
    }
#}

    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)   
```

Summary stats
```{r}
summary_BimodAudio_cond <- df_BimodAudio_summ_accu_cond %>% 
    group_by(group, cond) %>% 
    dplyr::summarise(
        mean = mean(accu_percent), 
        sd = mean(accu_percent)
    )

summary_BimodAudio_axis <- df_BimodAudio_summ_accu_cond_axis %>% 
    group_by(group, cond, axis) %>% 
    dplyr::summarise(
        mean = mean(accu_percent), 
        sd = mean(accu_percent)
    )
```


Anovas
```{r}
ANOVA_BimodalAudio_conditions <- ezANOVA(
    data = df_BimodAudio_summ_accu_cond,
    dv = accu_percent,
    wid = subject,
    within = cond,
    between = group)


ANOVA_BimodalAudio_conditions_axis <- ezANOVA(
    data = df_BimodAudio_summ_accu_cond_axis,
    dv = accu_percent,
    wid = subject,
    within = .(cond, axis), 
    between = group)

```


## BIMODAL MOTION VISUAL- MOTION VS STATIC
```{r}

subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionVis'
conditions <- c('visual_motion', 'visual_static')


#Prepare df to store group accuracy
df_bimodMotVis_sighted_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)
df_bimodMotVis_sighted_run_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        for(c in seq_along(conditions)){
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            #filter((!grepl('trigger', trial_type))) %>% 
             filter(trial_type == conditions[c] | trial_type == 'response') %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
            # 3 = static target / 2 = motion target? but only for sub 01 & 02
            # rest have 2.000 as a general audio target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                   '1.000000' = '0',
                                   '1' = '0',
                                   'n/a' = '0')) %>% 
            mutate(target_func = target)
        
        
        accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[2],
                                cond = conditions[c],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent) %>% 
                     mutate(cond = factor(cond, levels = c('visual_motion', 'visual_static')))
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        
        
        
        }
        
        #Add data to accuracies by RUN
        df_bimodMotVis_sighted_run_accu_cond <- rbind(df_bimodMotVis_sighted_run_accu_cond, sub_accu)
        
        
    }
    sub_accu_mean <- sub_accu %>% 
        group_by(cond) %>% 
        mutate(accu_percent = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotVis_sighted_summ_accu_cond<- rbind(df_bimodMotVis_sighted_summ_accu_cond, sub_accu_mean)
}
 
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)   
```
 

## BIMODAL MOTION VISUAL- CONDITION x AXIS
```{r}

subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionVis'
conditions <- c('visual_motion', 'visual_static')
axis_list <- c('vertical', 'horizontal') 

#Prepare df to store group accuracy
df_bimodMotVis_sighted_summ_accu_cond_axis <- data.frame(stringsAsFactors = FALSE)
df_bimodMotVis_sighted_run_accu_cond_axis <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])
    
    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                             pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                             recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        # MOTION VS STATIC
        for(c in seq_along(conditions)){
            
            # HORIZONTAL VS VERTICAL 
            for(a in seq_along(axis_list)){
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events
                    #filter((!grepl('trigger', trial_type))) %>% 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #keep given axis and responses (they have 'n/a in axis)
                    filter(axis == axis_list[a] | axis == 'n/a') %>% 
                    #mutate(target = as.numeric(target)) %>% 
                    #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
                    # 3 = static target / 2 = motion target? but only for sub 01 & 02
                    # rest have 2.000 as a general audio target
                    mutate(target = recode(target, '3' = '1', 
                                           '2' = '1',
                                           '2.000000' = '1',
                                           '1.000000' = '0',
                                           '1' = '0',
                                           'n/a' = '0')) %>% 
                    mutate(target_func = target)
                
                
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[2],
                                        cond = conditions[c],
                                        axis = axis_list[a],
                                        run_num = j,
                                        run_lab = paste0('run-0',j),
                                        task = task, 
                                        accu_percent = accu_percent) %>% 
                    mutate(cond = factor(cond, levels = c('visual_motion', 'visual_static')))
                #Add this run to subject data
            
                sub_accu <- rbind(sub_accu, accu_temp)
                
            
            
            #Add data to accuracies by RUN
            df_bimodMotVis_sighted_run_accu_cond_axis <-
                rbind(df_bimodMotVis_sighted_run_accu_cond_axis, sub_accu)
            }
        }
        
    }
    sub_accu_mean <- sub_accu %>% 
        group_by(cond, axis) %>% 
        mutate(accu_percent = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotVis_sighted_summ_accu_cond_axis<- rbind(df_bimodMotVis_sighted_summ_accu_cond_axis, sub_accu_mean)
}

#Small cleanup
rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)   
```
 


clean up
```{r}
rm(pairs, accu_temp, sub_accu, sub_accu_mean, temp_data, temp_data_clean)
```

## ----- PLOTS -----

Plots for each condition
```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))


dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

lab_aud <- c('Motion (A)', 'Static (A)')
lab_vis <- c('Motion (V)', 'Static (V)')


## AUDIO PLOTS
# AVERAGE
plot_BimodAudio_blind <- df_BimodAudio_summ_accu_cond %>% 
    filter(group == "EB") %>% 
    blam_accuracy_points_sum_conditions_group(., lab_aud, dark_colors[1])

plot_BimodAudio_sighted<- df_BimodAudio_summ_accu_cond %>% 
    filter(group == "SC") %>% 
    blam_accuracy_points_sum_conditions_group(., lab_aud, dark_colors[2])

plot_BimodAudio <- plot_BimodAudio_blind + plot_BimodAudio_sighted
rm(plot_Audio_V1_accu_run_blind, plot_Audio_V1_accu_run_sighted)

# BY RUN
plot_BimodAudio_accu_run_blind <- df_BimodAudio_run_accu_cond %>% 
    filter(group=='EB') %>% 
    blam_accuracy_points_run_cond(.)

plot_BimodAudio_accu_run_sighted <- df_BimodAudio_run_accu_cond %>% 
    filter(group=='SC') %>% 
    blam_accuracy_points_run_cond(.)

plot_BimodAudio_accu_run <- plot_BimodAudio_accu_run_blind + plot_BimodAudio_accu_run_sighted 
rm(plot_BimodAudio_accu_run_blind, plot_BimodAudio_accu_run_sighted)

## VISUAL PLOTS 
#AVERAGE
plot_BimodVis_sighted <- blam_accuracy_points_sum_conditions_group(df_bimodMotVis_sighted_summ_accu_cond, 
                                                                lab_vis, 
                                                                dark_colors[2])

#BY RUN
plot_BimodVis_accu_run_sighted <- df_bimodMotVis_sighted_run_accu_cond %>% 
    blam_accuracy_points_run_cond(.)

```


Plots for each CONDITION AND AXIS
```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))


dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

lab_axis <- c('Motion (Hor)', 'Motion (Vert)',  'Static (Hor)','Static(Vert)')


##
plot_BimodAudio_blind_axis <- df_BimodAudio_summ_accu_cond_axis %>% 
    filter(group == "EB") %>% 
    blam_accuracy_points_bimodal_axis(., lab_axis, dark_colors[1])

plot_BimodAudio_sighted_axis <- df_BimodAudio_summ_accu_cond_axis %>% 
    filter(group == "SC") %>% 
    blam_accuracy_points_bimodal_axis(., lab_axis, dark_colors[2])

plot_BimodalAudio_axis <- plot_BimodAudio_blind_axis + plot_BimodAudio_sighted_axis
rm(plot_BimodAudio_sighted_axis, plot_BimodAudio_blind_axis)


plot_BimodalVis_axis <-  blam_accuracy_points_bimodal_axis(df_bimodMotVis_sighted_summ_accu_cond_axis, lab_axis, dark_colors[2])

```


#----------------------------- TESTS ------------------------------




