---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho) #For d'
library(RColorBrewer)
library(cowplot)
library(patchwork)
library(ez)

```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
#tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
#           'task-bimodalMotionAud', 'task-bimodalMotionVis')
task <- 'audioV1'
#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')

accu_tw <- 3
#env cleanup
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))
rm(raw_repo)
```


## BLIND+SIGHTED AUDIO V1: average performance

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
sub_SC <- c('01','02','03','04', '06', '07')
sub_EB<- c('01','02','03','04', '05','07')


#Prepare df to store group accuracy
df_AudioV1_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(g in seq_along(groups)){
    for(i in seq_along(sub_SC)) {
        
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task 
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                                 recursive = TRUE)
        
        sub_accu <- data.frame(stringsAsFactors = FALSE)
        
        for(j in seq_along(sub_events)){
            
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                        sep = '/'), header=TRUE)
            
            
            # TRY TO ADD ANOTHER LOOP WITH CONDITIONS?
            
           # n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
            #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
            
            
            #Main subject df to wrangle, only one run now!
            temp_data_clean <- temp_data %>% 
                #get rid of trigger events
                filter((!grepl('trigger', trial_type))) %>% 
                mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
                mutate(oneBack = as.numeric(oneBack)) %>% 
                #Equalize target column name for function use
                mutate(target_func = oneBack)
            
            # Function call saves space! 
            accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
            
            #ADD METADATA to the temp df
            
            accu_temp <- data.frame(subject = bids_sub, group = groups[g],
                                    run_num = j,
                                    run_lab = paste0('run-0',j),
                                    task = task, 
                                    accu_percent = accu_percent)
            #Add this run to subject data
            sub_accu <- rbind(sub_accu, accu_temp)
            
            
            
        }
        
        #Add data to accuracies by RUN
        df_AudioV1_run_accu <- rbind(df_AudioV1_run_accu, sub_accu)
        
        sub_accu_mean <- sub_accu %>% 
            mutate(accu_percent  = mean(accu_percent)) %>% 
            dplyr::select(-c(run_lab, run_num)) %>% 
            slice(1)
        
        #Add data to accuracy summaries by subject
        df_AudioV1_summ_accu<- rbind(df_AudioV1_summ_accu, sub_accu_mean)
        
        
        #Small cleanup
        rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)     
    }
}
    

```



## BLIND + SIGHTED AUDIO V1: condition split 

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
sub_SC <- c('01','02','03','04', '06', '07')
sub_EB<- c('01','02','03','04', '05','07')
conditions <- c('object','voice','scrambled_object','scrambled_voice')

#Prepare df to store group accuracy
df_AudioV1_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_run_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(g in seq_along(groups)){
    for(i in seq_along(sub_SC)) {
        
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task 
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                                 recursive = TRUE)
        
        sub_accu <- data.frame(stringsAsFactors = FALSE)
        
        for(j in seq_along(sub_events)){
            
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                        sep = '/'), header=TRUE)
            
            for(c in seq_along(conditions)){
                
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events
                    filter(trial_type == conditions[c] | trial_type == 'response') %>%  
                    mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
                    mutate(oneBack = as.numeric(oneBack)) %>% 
                    #Equalize target column name for function use
                    mutate(target_func = oneBack)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                        cond = conditions[c],
                                        run_num = j,
                                        run_lab = paste0('run-0',j),
                                        task = task, 
                                        accu_percent = accu_percent)
                #Add this run to subject data
                sub_accu <- rbind(sub_accu, accu_temp)
                
            }   
            
            #Add data to accuracies by RUN
            df_AudioV1_run_accu_cond <- rbind(df_AudioV1_run_accu_cond, sub_accu)
            
        }     
        
        sub_accu_mean <- sub_accu %>% 
            group_by(cond) %>% 
            mutate(accu_percent = mean(accu_percent)) %>% 
            mutate(cond = factor(cond, levels = c('object', 
                                                  'voice', 
                                                  'scrambled_object', 
                                                  'scrambled_voice'))) %>% 
            dplyr::select(-c(run_lab, run_num)) %>% 
            slice(1)
        
        #Add data to accuracy summaries by subject
        df_AudioV1_summ_accu_cond<- rbind(df_AudioV1_summ_accu_cond, sub_accu_mean)
        
    }
}

#Small cleanup    
rm(accu_temp,sub_accu, sub_accu_mean, temp_data, temp_data_clean)   

```

Make summary DF with group stats
```{r}
#ALL DATA
df_AudioV1_group_conditions <- df_AudioV1_summ_accu_cond %>% 
    group_by(group, cond) %>% 
    dplyr::summarise(mean = mean(accu_percent),
                     sd = sd(accu_percent))

#NO OUTLIERS
df_AudioV1_group_conditions_clean <- df_AudioV1_summ_accu_cond %>% 
    filter(subject != 'sub-EB02' & subject != 'sub-SC06') %>% 
    group_by(group, cond) %>% 
    dplyr::summarise(mean = mean(accu_percent),
                     sd = sd(accu_percent))



ANOVA_conditions <- ezANOVA(
    data = df_AudioV1_summ_accu_cond,
    dv = accu_percent,
    wid = subject,
    within = cond,
    between = group)
```


## ----- PLOTS -----

Average Plots (across conditions)
```{r}
#Group SUM
#source plotting functions
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))
 
## ONE BIG AVERAGE
plot_AudioV1_accu <- blam_accuracy_points_sum(df_AudioV1_summ_accu) + 
    theme(legend.position = 'none')

##SPLIT BY RUNS
plot_Audio_V1_accu_run_blind <- df_AudioV1_run_accu %>% 
    filter(group=='EB') %>% 
    blam_accuracy_points_run(.)

plot_Audio_V1_accu_run_sighted <- df_AudioV1_run_accu %>% 
    filter(group=='SC') %>% 
    blam_accuracy_points_run(.)

plot_Audio_V1_accu_run_blind+plot_Audio_V1_accu_run_sighted
#plot_Audio_V1_accu_run_sighted
```

Plots for each condition
```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))


dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

lables <- c('O', 'V', 'ScO', 'ScV')


plot_AudioV1_blind_accu_cond <- df_AudioV1_summ_accu_cond %>% filter(group=='EB') %>% 
    blam_accuracy_points_sum_conditions_group(., lables, dark_colors[1])

plot_AudioV1_sighted_accu_cond <- df_AudioV1_summ_accu_cond %>% filter(group=='SC') %>% 
    blam_accuracy_points_sum_conditions_group(., lables, dark_colors[2])

plot_AudioV1_accu_cond <- plot_AudioV1_blind_accu_cond + plot_AudioV1_sighted_accu_cond
rm(plot_AudioV1_blind_accu_cond,plot_AudioV1_sighted_accu_cond)


## REMOVE OUTLIERS
plot_AudioV1_blind_accu_cond_clean <- df_AudioV1_summ_accu_cond %>% 
    filter(group=='EB' & subject != 'sub-EB02') %>% 
    blam_accuracy_points_sum_conditions_group(., lables, dark_colors[1])

plot_AudioV1_sighted_accu_cond_clean <- df_AudioV1_summ_accu_cond %>% 
    filter(group=='SC' & subject != 'sub-SC06') %>% 
    blam_accuracy_points_sum_conditions_group(., lables, dark_colors[2])

plot_AudioV1_accu_cond_clean <- plot_AudioV1_blind_accu_cond_clean + plot_AudioV1_sighted_accu_cond_clean
rm(plot_AudioV1_blind_accu_cond_clean,plot_AudioV1_sighted_accu_cond_clean)
```

