---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to soundTargets

1.  Auditory motion localizer (Blind + Sighted)
2.  Visual motion localizer (Sighted)
3.  MST localizer (Sighted)

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)
library(patchwork)
```

# Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script

#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)


#This is the WIDTH of the time window for accuracy, i.e. responses will be bound to targets if they occurr within that TW
accu_tw <- 3
#env cleanup
rm(raw_repo)

## Source the functions 
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))
```

# AUDIO LOCALIZER

## Blind + Sighted
```{r}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
#sub_EB <- c('01','03','04', '05','06','07')
#sub_SC <- c('02','03','04', '05','06', '07')

## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER

sub_SC <- c('01','02','03','04', '06', '07')
sub_EB<- c('01','02','03','04', '05','07')
groups <- c('EB', 'SC')
task <- 'auditoryLocalizer'
conditions <- c('motion','static')

# Prepare an empty df 
df_AudioLoc_accu_cond <- data.frame(stringsAsFactors = FALSE)


#Loop across subjects 
for(g in seq_along((groups))){
    for(i in seq_along(sub_SC)) {
        
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task
        # get rid of what looks like field map events?
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                  task, '.*',
                                                  "_events\\.tsv$"),
                                 recursive = TRUE) %>%
            str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
            str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
        
        #For some reason EB03 & SC02 have 2 runs of AudioLocalizer?
        # For sub-EB03 take the one from ses-02
        # For sub-SC02 take the one from ses-03, BUT WE DON'T KNOW WHY
        # and maybe we will change it to the first one!
            
        if(bids_sub == 'sub-EB03' | bids_sub == 'sub-SC02' ){
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[2],
                                        sep = '/'), header=TRUE)
        }else{
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[1],
                                        sep = '/'), header=TRUE)}
            
            
            for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pic given condition! 
                    filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #drop first event which is always flagged as a target?
                   # slice(-1) %>% 
                    mutate(soundTarget = recode(soundTarget, 'n/a' = '0')) %>% 
                    mutate(soundTarget = as.numeric(soundTarget)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = soundTarget)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                        cond = conditions[c],
                                        task = task, 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_AudioLoc_accu_cond <- rbind(df_AudioLoc_accu_cond, accu_temp)
                
            }
        
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_AudioLoc <- df_AudioLoc_accu_cond %>% 
    #filterout outliers :) 
    filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    group_by(group, cond) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )
```

## Blind + Sighted: Fixation targets
```{r}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
#sub_EB <- c('01','03','04', '05','06','07')
#sub_SC <- c('02','03','04', '05','06', '07')

## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER

sub_SC <- c('01','02','03','04', '06', '07')
#sub_EB<- c('01','02','03','04', '05','07')
groups <- c('SC')
task <- 'auditoryLocalizer'
#conditions <- c('motion','static')

# Prepare an empty df 
df_AudioLoc_accu_FIX <- data.frame(stringsAsFactors = FALSE)


#Loop across subjects 
for(g in seq_along((groups))){
    for(i in seq_along(sub_SC)) {
        
        #Pick a subject from correct list 
        if(groups[g]=='EB'){
            bids_sub <- paste0('sub-',groups[g],sub_EB[i])
        }else if(groups[g]=='SC'){
            bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        }
        
        #Grab events from this sub in this task
        # get rid of what looks like field map events?
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                  task, '.*',
                                                  "_events\\.tsv$"),
                                 recursive = TRUE) %>%
            str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
            str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
        
        #For some reason EB03 & SC02 have 2 runs of AudioLocalizer?
        # For sub-EB03 take the one from ses-02
        # For sub-SC02 take the one from ses-03, BUT WE DON'T KNOW WHY
        # and maybe we will change it to the first one!
            
        if(bids_sub == 'sub-EB03' | bids_sub == 'sub-SC02' ){
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[2],
                                        sep = '/'), header=TRUE)
        }else{
            temp_data<-read.table(paste(inputs, bids_sub, sub_events[1],
                                        sep = '/'), header=TRUE)}
            
            
            #for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pic given condition! 
                   # filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                    #drop first event which is always flagged as a target?
                   # slice(-1) %>% 
                    mutate(fixationTarget = recode(fixationTarget, 'n/a' = '0')) %>% 
                    mutate(fixationTarget = as.numeric(fixationTarget)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = fixationTarget)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                       # cond = conditions[c],
                                        task = task, 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_AudioLoc_accu_FIX <- rbind(df_AudioLoc_accu_FIX, accu_temp)
                
         #   }
        
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_AudioLoc_FIX <- df_AudioLoc_accu_FIX %>% 
    #filterout outliers :) 
    #filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    #group_by(group, cond) %>% 
    group_by(group) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )
```




# VISUAL LOCALIZERS 
Both Vis + MT / MST
```{r}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
#sub_EB <- c('01','03','04', '05','06','07')
#sub_SC <- c('02','03','04', '05','06', '07')

## TEST THE SCRIPT WITH ALL SUBJECTS PARTICIPATING IN THE STUDY! 
# IF YOU WANT TO EXCLUDE THE OBVIOUS OUTLIERS, YOU CAN ALSO DO IT LATER



# WHERE ARE THE EVENT FILES FROM sub-SC04?!
sub_SC <- c('01','02','03','04', '05','06', '07')

task <- c('visualLocalizer','mtMstLocalizer')
#conditions <- c('motion','static')

# Prepare an empty df 
df_VisualLoc_accu <- data.frame(stringsAsFactors = FALSE)

groups <- 'SC'

#Loop across subjects 
for(g in seq_along((groups))){
    for(i in seq_along(sub_SC)) {
        
        
        bids_sub <- paste0('sub-',groups[g],sub_SC[i])
        
        for(t in seq_along(task)){
            
            #Grab events from this sub in this task
            # get rid of what looks like field map events?
            sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                     pattern = paste0(bids_sub,'_.*_' ,'task-',
                                                      task[t], '.*',
                                                      "_events\\.tsv$"),
                                     recursive = TRUE) %>%
                str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
                str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
            
            
            for(j in seq_along(sub_events)){
                
                temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                            sep = '/'), header=TRUE)
                
                
                #for(c in seq_along(conditions)){
                
                #Main subject df to wrangle, only one run now!
                temp_data_clean <- temp_data %>% 
                    #get rid of trigger events and only pic given condition! 
                    filter((!grepl('trigger', trial_type))) %>% 
                    #drop first event which is always flagged as a target?
                    # slice(-1) %>% 
                    mutate(target = recode(target, 'n/a' = '0')) %>% 
                    mutate(target = as.numeric(target)) %>% 
                    #Unify target column names for function to work! 
                    mutate(target_func = target)
                
                # Function call saves space! 
                accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
                
                #ADD METADATA to the temp df
                
                accu_temp <- data.frame(subject = bids_sub, 
                                        group = groups[g],
                                        #condition = conditions[c],
                                        task = task[t], 
                                        accu_percent = accu_percent)
                
                #Add this subject to group data
                df_VisualLoc_accu <- rbind(df_VisualLoc_accu, accu_temp)
                
            }
        }
    }
}

#Clean up
rm(accu_temp, temp_data, temp_data_clean)

# Calculate group averages and SDs
df_group_VisualLoc <- df_VisualLoc_accu %>% 
    #filterout outliers :) 
    #filter(subject != 'sub-EB02' & subject != 'sub-SC01') %>% 
    group_by(task) %>% 
    dplyr::summarise(
        mean_accu = mean(accu_percent),
        sd_accu = sd(accu_percent)
    )
```


# PLOTS! 

```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

labels_aud <- c('Motion (A)', 'Static (A)')

labels_vis <- c('Vis Loc', 'MT/MST Loc')

## DFs: remove outliers! 
df_AudioLoc_accu_cond_blind <- df_AudioLoc_accu_cond %>% 
    filter(group == 'EB' & subject != 'sub-EB02')
df_AudioLoc_accu_cond_sighted <- df_AudioLoc_accu_cond %>% 
    filter(group == 'SC' & subject != 'sub-SC01')


df_VisualLoc_accu_plot <- df_VisualLoc_accu %>% 
    mutate(cond = task)

## PLOT AUDIO 
plot_Audio_blind <- blam_accuracy_points_sum_conditions_group(df_AudioLoc_accu_cond_blind, 
                                                              labels_aud, 
                                                              dark_colors[1]) +
    scale_y_continuous(name = 'Accuracy [%]', 
                       limits = c(35,100))

plot_Audio_sig <- blam_accuracy_points_sum_conditions_group(df_AudioLoc_accu_cond_sighted, 
                                                              labels_aud, 
                                                              dark_colors[2])+
    scale_y_continuous(name = 'Accuracy [%]', 
                       limits = c(35,100))

plot_AudioLoc <- plot_Audio_blind  + plot_Audio_sig

#BONUS: PLOT AUDIO FOR FIX TARGETS COLOR CHANGES IN SIGHTED
plot_Audio_fix_sig <- blam_accuracy_points_sum_group(df_AudioLoc_accu_FIX, dark_colors[2])

rm(plot_Audio_blind, plot_Audio_sig)

## PLOT VISUAL 
plot_VisualLoc <- blam_accuracy_points_sum_conditions_group(df_VisualLoc_accu_plot, 
                                                              labels_vis, 
                                                              dark_colors[2])
```











##--------------------------  ARCHIVE -----------------------------------------
## SMALL LOOP TEST! 


```{r}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
subjects <- c('01','03','04', '05','06','07')
task <- 'auditoryLocalizer'
group <- 'EB'


df_AudioLoc_blind_accu <- data.frame(stringsAsFactors = FALSE)




#Loop across subjects 
for(i in seq_along(subjects)) {
    
    bids_sub <- paste0('sub-',groups[1],subjects[i])
    
    #Grab events from this sub in this task
    # get rid of what looks like field map events?
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                             pattern = paste0(bids_sub,'_.*_' ,'task-',
                                              task, '.*',
                                              "_events\\.tsv$"),
                             recursive = TRUE) %>%
        str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
        str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
    
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            #mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '0')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) %>% 
            #Unify target column names for function 
            mutate(target_func = soundTarget)
        
        # Function call saves space! 
        accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
        
        #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                condition = 'average',
                                task = tasks[2], accu_percent = 
                                    accu_percent)
        
        #Add this subject to group data
        df_AudioLoc_blind_accu <- rbind(df_AudioLoc_blind_accu, accu_temp)
        
        
    }
}

```

## SMALL LOOP TEST: CONDITIONS


```{r}
# Grab the analyses functions
source(paste(project_path, 'code','src','BLAM_functions_analyses.R', sep = '/'))


# define variables for this task
subj <- c('01','03','04', '05','06','07')
task <- 'auditoryLocalizer'
conditions <- c('motion','static')
#group <- 'EB'


df_AudioLoc_blind_accu_cond <- data.frame(stringsAsFactors = FALSE)


#Loop across subjects 
for(i in seq_along(subjects)) {
    
    bids_sub <- paste0('sub-',groups[1],subjects[i])
    
    #Grab events from this sub in this task
    # get rid of what looks like field map events?
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                             pattern = paste0(bids_sub,'_.*_' ,'task-',
                                              task, '.*',
                                              "_events\\.tsv$"),
                             recursive = TRUE) %>%
        str_subset(pattern = ".*_part-mag_events\\.tsv$", negate = TRUE) %>%
        str_subset(pattern = ".*_part-phase_events\\.tsv$",negate = TRUE)
    
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        
        for(c in seq_along(conditions)){
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter(trial_type == conditions[c] | trial_type == 'response') %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            #mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '0')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) %>% 
            #Unify target column names for function 
            mutate(target_func = soundTarget)
        
        # Function call saves space! 
        accu_percent <- blam_accuracy_tw(temp_data_clean, accu_tw)
        
        #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                condition = conditions[c],
                                task = tasks[2], accu_percent = 
                                    accu_percent)
        
        #Add this subject to group data
        df_AudioLoc_blind_accu_cond <- rbind(df_AudioLoc_blind_accu_cond, accu_temp)
        
        }
    }
}

```

