---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

1.  Auditory motion localizer
2.  Visual motion localizer
3.  Bimidal motion auditory
4.  Bimodal motion visual
5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
library(psycho)
```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
           'task-bimodalMotionAud', 'task-bimodalMotionVis')

#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')
#env cleanup
rm(raw_repo)
```

Start slowly with Audio motion localizer, just one test subject Then put it into loops

## BLIND AUDIO LOCALIZER

```{r}

#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO
# sub-EB02 did not respond at all in this task so is excluded
subject <- c('01','03','04', '05','06','07')


#Prepare df to store group accuracy
df_AudioLoc_blind_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    #Sub EB01 & EB02 doesn't have _run-01_ in sequence name...
    if(bids_sub == 'sub-EB01'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_events\\.tsv$"), 
                         recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_run-01_events\\.tsv$"), 
                         recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) 
        
        # extract pairs between trial_types to look for 2 types: 
        #   hits = target (1) followed by a response (2)
        #   false alarms = non-target(0) followed by a response(2)
        #   misses = target (1) followed by no response (0)
        #   correct rejections = (0) followed by (0) + (0) followed by (1)   
            
            
            pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
                                second = tail(temp_data_clean$soundTarget, -1))
            temp_tab <- table(pairs)
            
            #D PRIME ANALYSES: most likely have to be ditched since sighted 
            #subjects are performing TWO tasks at once and false alarms make 
            #no sense, so only count soundTarget hits and misses for between-group
            #consistency. 
            #leaving dprimes for future inspiration though
            
            hit <- temp_tab[2,3]
           # fa <- temp_tab[1,3]
           # miss <- temp_tab[2,1]
            # corr_rej <- temp_tab[1,1] + temp_tab[1,2]
            
           # dprime.stats<-psycho::dprime(hit, fa, miss, corr_rej)
            
            #dprime <- dprime.stats$dprime
            
            accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                
                                task = tasks[2], accu_percent = 
                                    accu_percent)
            
        #Add this subject to group data
        
        df_AudioLoc_blind_accu <- rbind(df_AudioLoc_blind_accu, accu_temp)
        
        #clean up
        #rm(accu_temp)
    }
          #rm(temp_data, temp_data_clean, pairs, temp_tab, hit, fa, miss, corr_rej,
          # sub_events, n_responses, n_targets, bids_sub, accu_percent, dprime, i,j)
}
    
rm(pairs, temp_data, accu_temp, temp_data_clean)    

```

## SIGHTED AUDIO LOCALIZER

```{r}

#Sighted subjects 
#sub-SC01 + sub-SC-07 responded only to fix crosses, so was awake 
subject <- c('02','03','04', '05','06')


#Prepare df to store group accuracy
df_AudioLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    if(bids_sub == 'sub-SC01' | bids_sub == 'sub-SC02'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_events\\.tsv$"), 
                         recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_run-01_events\\.tsv$"), 
                         recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) 
        
        # extract pairs between trial_types to look for 2 types: 
        #   hits = target (1) followed by a response (2)
        #   false alarms = non-target(0) followed by a response(2)
        #   misses = target (1) followed by no response (0)
        #   correct rejections = (0) followed by (0) + (0) followed by (1)   
            
            
            pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
                                second = tail(temp_data_clean$soundTarget, -1))
            temp_tab <- table(pairs)
            
            #D PRIME ANALYSES: most likely have to be ditched since sighted 
            #subjects are performing TWO tasks at once and false alarms make 
            #no sense, so only count soundTarget hits and misses for between-group
            #consistency. 
            #leaving dprimes for future inspiration though
            
            hit <- temp_tab[2,3]
           # fa <- temp_tab[1,3]
           # miss <- temp_tab[2,1]
            # corr_rej <- temp_tab[1,1] + temp_tab[1,2]
            
           # dprime.stats<-psycho::dprime(hit, fa, miss, corr_rej)
            
            #dprime <- dprime.stats$dprime
            
            accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                
                                task = tasks[2], accu_percent = 
                                    accu_percent)
            
        #Add this subject to group data
        
        df_AudioLoc_sighted_accu <- rbind(df_AudioLoc_sighted_accu, accu_temp)
        
        #clean up

    }

}
    
rm(pairs, temp_data, accu_temp, temp_data_clean)        

```

## SIGHTED VISUAL LOCALIZER

```{r}
#Sighted subjects 
#sub-SC01 responded only to fix crosses, so was awake 
subject <- c('01','02','03','04', '05', '06', '07')


#Prepare df to store group accuracy
df_VisualLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    if(bids_sub == 'sub-SC01' | bids_sub == 'sub-SC02'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[3], "_events\\.tsv$"), 
                         recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                         pattern = paste0(bids_sub,'_.*_' ,tasks[3], "_run-01_events\\.tsv$"), 
                         recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$target), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            mutate(target = recode(target, 'n/a' = '2')) %>% 
            mutate(target = as.numeric(target)) 
        
        # extract pairs between trial_types to look for 2 types: 
        #   hits = target (1) followed by a response (2)
        #   false alarms = non-target(0) followed by a response(2)
        #   misses = target (1) followed by no response (0)
        #   correct rejections = (0) followed by (0) + (0) followed by (1)   
            
            
            pairs <- data.frame(first = head(temp_data_clean$target, -1), 
                                second = tail(temp_data_clean$target, -1))
            temp_tab <- table(pairs)
            
            #D PRIME ANALYSES: most likely have to be ditched since sighted 
            #subjects are performing TWO tasks at once and false alarms make 
            #no sense, so only count soundTarget hits and misses for between-group
            #consistency. 
            #leaving dprimes for future inspiration though
            
            hit <- temp_tab[2,3]
           # fa <- temp_tab[1,3]
           # miss <- temp_tab[2,1]
            # corr_rej <- temp_tab[1,1] + temp_tab[1,2]
            
           # dprime.stats<-psycho::dprime(hit, fa, miss, corr_rej)
            
            #dprime <- dprime.stats$dprime
            
            accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                
                                task = tasks[3], accu_percent = 
                                    accu_percent)
            
        #Add this subject to group data
        
        df_VisualLoc_sighted_accu <- rbind(df_VisualLoc_sighted_accu, accu_temp)
        
        #clean up

    }
          rm(temp_data, temp_data_clean, pairs, temp_tab, hit, fa, miss, corr_rej,
           sub_events, n_responses, n_targets, bids_sub, accu_percent, dprime, i,j)
}
    
    

```

## BLIND AUDIO V1

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03','04', '05','07')


#Prepare df to store group accuracy
df_AudioV1_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[1], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '2')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
            
            
            pairs <- data.frame(first = head(temp_data_clean$oneBack, -1), 
                                second = tail(temp_data_clean$oneBack, -1))
            temp_tab <- table(pairs)
            
            hit <- temp_tab[2,3]
 
            
        accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                run = paste0('run-0',j),
                                task = tasks[1], accu_percent = 
                                    accu_percent)
        
        sub_accu <- rbind(sub_accu, accu_temp)
        #Add this subject to group data
        
        
        
        #clean up

    }
         # rm(temp_data, temp_data_clean, pairs, temp_tab, hit, fa, miss, corr_rej,
         #  sub_events, n_responses, n_targets, bids_sub, accu_percent, dprime, i,j)
    
    #Add data to accuracies by RUN
    df_AudioV1_blind_run_accu <- rbind(df_AudioV1_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_blind_summ_accu<- rbind(df_AudioV1_blind_summ_accu, sub_accu_mean)
    
}
    
    

```

## SIGHTED AUDIO V1

```{r}
#List of subjects for this particular task

# This has to go by runs 
subject <- c('01','02','03','04', '05','06','07')


#Prepare df to store group accuracy
df_AudioV1_sighted_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_sighted_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[1], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
       # n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '2')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
            
            
            pairs <- data.frame(first = head(temp_data_clean$oneBack, -1), 
                                second = tail(temp_data_clean$oneBack, -1))
            temp_tab <- table(pairs)
            
            hit <- temp_tab[2,3]
 
            
        accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                run = paste0('run-0',j),
                                task = tasks[1], accu_percent = 
                                    accu_percent)
        
        sub_accu <- rbind(sub_accu, accu_temp)
        
        

    }
 
    df_AudioV1_sighted_run_accu <- rbind(df_AudioV1_sighted_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_sighted_summ_accu<- rbind(df_AudioV1_sighted_summ_accu, sub_accu_mean)
    
    
      #  rm(temp_data, temp_data_clean, pairs, temp_tab, hit,
      #    sub_events, n_responses, n_targets, bids_sub, accu_percent, i,j,
      #    sub_accu, sub_accu_mean, accu_temp)
}
    
    

```

## ----- PLOTS -----

get the stuff that you need

```{r}
library(RColorBrewer)
library(cowplot)
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))
```

LOCALIZERS

```{r}

#subject, group, task, accu_percent

plot_AudioLoc_accu <- blam_accuracy_points_sum(rbind(df_AudioLoc_blind_accu, df_AudioLoc_sighted_accu))

#still missing data from sub-SC04
plot_VisualLoc_accu <- blam_accuracy_points_sum_visloc(df_VisualLoc_sighted_accu)

```

AUDIO V1 TASK

```{r}
#Group SUM


df_AudioV1_summ_plot <- rbind(df_AudioV1_blind_summ_accu,
                                              df_AudioV1_sighted_summ_accu) %>% 
    mutate(accu_percent = mean_accu)

plot_AudioV1_accu <- blam_accuracy_points_sum(df_AudioV1_summ_plot)

#facet by subjects to show runs
df_AudioV1_run_plot <- rbind(df_AudioLoc_blind_run_accu, df_AudioLoc_sighted_run_accu)
```

----- TESTS ----- Bimodal motion (audio, blind)

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03','04', '05','06','07')

#Prepare df to store group accuracy
df_bimodalMotAud_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_bimodalMotAud_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[4], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE) 
        
       
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #mutate(target = as.numeric(target)) %>% 
            #recode from 3 to 1 to get proper n of targets
            # wait this might be iportant for 2 tasks! 
            #mutate(target = recode(target, "3" = "1", '2' = '1')) %>% 
            mutate(target = recode(target, 'n/a' = '2')) %>% 
            mutate(target = as.numeric(target)) 
            
            
            pairs <- data.frame(first = head(temp_data_clean$target, -1), 
                                second = tail(temp_data_clean$target, -1))
            temp_tab <- table(pairs)
            
            hit <- temp_tab[2,3]
 
            n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()           
        accu_percent <- (hit/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                run = paste0('run-0',j),
                                task = tasks[4], accu_percent = 
                                    accu_percent)
        
        sub_accu <- rbind(sub_accu, accu_temp)
        #Add this subject to group data
        
        
        
        #clean up

    }
 
    
    #Add data to accuracies by RUN
    df_AbimodalMotAud_blind_run_accu <- rbind(df_bimodalMotAud_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodalMotAud_blind_summ_accu<- rbind(df_bimodalMotAud_blind_summ_accu, sub_accu_mean)
    
    
        rm(temp_data, temp_data_clean, pairs, temp_tab, hit,
          sub_events, n_responses, n_targets, bids_sub, accu_percent, i,j,
          sub_accu, sub_accu_mean, accu_temp)
}
    
    

```
