---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

1.  Auditory motion localizer
2.  Visual motion localizer
3.  Bimidal motion auditory
4.  Bimodal motion visual
5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

## TO DO AFTER SUMMARY MEETING: 
- restructure the script to look for responses based on the width of the TIME WINDOW
instead of neighbouring trials (target followed by response)

- divide trials and accuracy into subgroups based on conditions (to see if the beh. 
performance is balanced across conditions)

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)
```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
           'task-bimodalMotionAud', 'task-bimodalMotionVis')

#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')

#This is the WIDTH of the time window for accuracy, i.e. responses will be bound to targets if they occurr within that TW
accu_tw <- 2
#env cleanup
rm(raw_repo)
```

Start slowly with Audio motion localizer, just one test subject Then put it into loops

## BLIND AUDIO LOCALIZER: NEIGHBOURING EVENTS ONLY

```{r}

#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO
# sub-EB02 did not respond at all in this task so is excluded
# subject <- c('01','03','04', '05','06','07')
# 
# 
# #Prepare df to store group accuracy
# df_AudioLoc_blind_accu <- data.frame(stringsAsFactors = FALSE)
# 
# #Loop across subjects 
# for(i in seq_along(subject)) {
#     
#     bids_sub <- paste0('sub-',groups[1],subject[i])
# 
#     #Grab events from this sub in this task 
#     #Sub EB01 & EB02 doesn't have _run-01_ in sequence name...
#     if(bids_sub == 'sub-EB01'){
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_events\\.tsv$"), 
#                          recursive = TRUE)
#     }else{
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[2],
#                                           "_run-01_events\\.tsv$"), 
#                          recursive = TRUE)}
#     
#     for(j in seq_along(sub_events)){
#           
#         temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
#                                 sep = '/'), header=TRUE)
#         
#         n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
#         #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
#         
#         #Main subject df to wrangle, only one run now!
#         temp_data_clean <- temp_data %>% 
#             #get rid of trigger events
#             filter((!grepl('trigger', trial_type))) %>% 
#             #drop first event which is always flagged as a target
#             slice(-1) %>% 
#             mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
#             mutate(soundTarget = as.numeric(soundTarget)) 
# 
#             #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
#             pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
#                                 second = tail(temp_data_clean$soundTarget, -1))
#             temp_tab <- table(pairs)
#             
#             
#             accu_percent <- (temp_tab[2,3]/n_targets)*100   
#             
#             #ADD METADATA to the temp df
#         
#         accu_temp <- data.frame(subject = bids_sub, group = groups[1],
#                                 
#                                 task = tasks[2], accu_percent = 
#                                     accu_percent)
#             
#         #Add this subject to group data
#         df_AudioLoc_blind_accu <- rbind(df_AudioLoc_blind_accu, accu_temp)
#         
# 
#     }
# }
#     
# rm(pairs, temp_data, accu_temp, temp_data_clean)    

```


## BLIND AUDIO LOCALIZER: TIME WINDOW ANALYSES
In the blind group, focus only on the SoundTargets
Test the width of the time window to answer

```{r}

#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO
# sub-EB02 did not respond at all in this task so is excluded
subject <- c('01','03','04', '05','06','07')


#Prepare df to store group accuracy
df_AudioLoc_blind_accu <- data.frame(stringsAsFactors = FALSE)



#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])
    
    #Grab events from this sub in this task 
    #Sub EB01 & EB02 doesn't have _run-01_ in sequence name...
    if(bids_sub == 'sub-EB01'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[2],
                                                  "_events\\.tsv$"), 
                                 recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[2],
                                                  "_run-01_events\\.tsv$"), 
                                 recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        #Sometimes first event is flagged as target, which is impossible. 
        # If that's the case, drop it from the number of targets
        if(as.numeric(temp_data$soundTarget[1]) == 1){
             n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
        } else {
            n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)
        }
       
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            #mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '0')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) 
        
        #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
        #pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
         #                   second = tail(temp_data_clean$soundTarget, -1))
        #temp_tab <- table(pairs)
        
        
        ## NEW SOLUTION: HOW TO FIND THE RESPONSES WITHIN THE TW? 
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$soundTarget[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                   temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                  #  hit <- 0
                  #  temp_hits <- c(temp_hits, hit)
                #}
               
            } 
        }
        
        
        #accu_percent <- (temp_tab[2,3]/n_targets)*100 
        accu_percent <- (sum(temp_hits)/n_targets)*100
        
        #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                
                                task = tasks[2], accu_percent = 
                                    accu_percent)
        
        #Add this subject to group data
        df_AudioLoc_blind_accu <- rbind(df_AudioLoc_blind_accu, accu_temp)
        
        
    }
}
    
rm(tw_data, temp_data, accu_temp, temp_data_clean)    

```

## SIGHTED AUDIO LOCALIZER

```{r}

# #Sighted subjects 
# #sub-SC01 + sub-SC-07 responded only to fix crosses, so was awake 
# subject <- c('01','02','03','04', '05','06', '07')
# 
# 
# #Prepare df to store group accuracy
# df_AudioLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)
# 
# #Loop across subjects 
# for(i in seq_along(subject)) {
#     
#     bids_sub <- paste0('sub-',groups[2],subject[i])
# 
#     #Grab events from this sub in this task 
#     if(bids_sub == 'sub-SC01' | bids_sub == 'sub-SC02'){
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_events\\.tsv$"), 
#                          recursive = TRUE)
#     }else if (bids_sub == 'sub-SC07') {
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_run-02_events\\.tsv$"), 
#                          recursive = TRUE)
#     }else{
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[2], "_run-01_events\\.tsv$"), 
#                          recursive = TRUE)}
#     
#     for(j in seq_along(sub_events)){
#           
#         temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
#                                 sep = '/'), header=TRUE)
#         
#         n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
#         #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
#         
#         #Main subject df to wrangle, only one run now!
#         temp_data_clean <- temp_data %>% 
#             #get rid of trigger events
#             filter((!grepl('trigger', trial_type))) %>% 
#             #drop first event which is always flagged as a target
#             slice(-1) %>% 
#             mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
#             mutate(soundTarget = as.numeric(soundTarget)) 
#             
#             #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
#             pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
#                                 second = tail(temp_data_clean$soundTarget, -1))
#             temp_tab <- table(pairs)
#             
#             accu_percent <- (temp_tab[2,3]/n_targets)*100   
#             
#             #ADD METADATA to the temp df
#         
#             accu_temp <- data.frame(subject = bids_sub, group = groups[2],
#                                 
#                                 task = tasks[2], accu_percent = 
#                                     accu_percent)
#             
#         #Add this subject to group data
#         df_AudioLoc_sighted_accu <- rbind(df_AudioLoc_sighted_accu, accu_temp)
#         
#         #clean up
# 
#     }
# 
# }
#     
# rm(pairs, temp_data, accu_temp, temp_data_clean)        

```


## SIGHTED AUDIO LOCALIZER: TW
```{r}
#Sighted subjects 
#sub-SC01 + sub-SC-07 responded only to fix crosses, so was awake 
subject <- c('01','02','03','04', '05','06', '07')


#Prepare df to store group accuracy
df_AudioLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)



#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])
    
    #Grab events from this sub in this task 
    #Sub EB01 & EB02 doesn't have _run-01_ in sequence name...
    if(bids_sub == 'sub-SC01'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[2],
                                                  "_events\\.tsv$"), 
                                 recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[2],
                                                  "_run-01_events\\.tsv$"), 
                                 recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        #Sometimes first event is flagged as target, which is impossible. 
        # If that's the case, drop it from the number of targets
        if(as.numeric(temp_data$soundTarget[1]) == 1){
             n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)-1
        } else {
            n_targets <- sum(as.numeric(temp_data$soundTarget), na.rm = TRUE)
        }
       
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            #mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(soundTarget = as.numeric(soundTarget)) 
        
        #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
        #pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
         #                   second = tail(temp_data_clean$soundTarget, -1))
        #temp_tab <- table(pairs)
        
        
        ## NEW SOLUTION: HOW TO FIND THE RESPONSES WITHIN THE TW? 
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$soundTarget[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                   temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                  #  hit <- 0
                  #  temp_hits <- c(temp_hits, hit)
                #}
               
            } 
        }
        
        
        #accu_percent <- (temp_tab[2,3]/n_targets)*100 
        accu_percent <- (sum(temp_hits)/n_targets)*100
        
        #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                
                                task = tasks[2], accu_percent = 
                                    accu_percent)
        
        #Add this subject to group data
        df_AudioLoc_sighted_accu <- rbind(df_AudioLoc_sighted_accu, accu_temp)
        
        
    }
}
    
rm(tw_data, temp_data, accu_temp, temp_data_clean)  
```


## SIGHTED VISUAL LOCALIZER

```{r}
#Sighted subjects 
#sub-SC01 responded only to fix crosses, so was awake 
# subject <- c('01','02','03','04', '05', '06', '07')
# 
# 
# #Prepare df to store group accuracy
# df_VisualLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)
# 
# #Loop across subjects 
# for(i in seq_along(subject)) {
#     
#     bids_sub <- paste0('sub-',groups[2],subject[i])
# 
#     #Grab events from this sub in this task 
#     # SC01 + SC02 do not have "run" in task name
#     # SC07 had localizer reran with run-02 due to technical issues
#     if (bids_sub == 'sub-SC01') {
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[3], "_events\\.tsv$"), 
#                          recursive = TRUE)
#     }else {
#         sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
#                          pattern = paste0(bids_sub,'_.*_' ,tasks[3], "_run-01_events\\.tsv$"), 
#                          recursive = TRUE)}
#     
#     for(j in seq_along(sub_events)){
#           
#         temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
#                                 sep = '/'), header=TRUE)
#         
#         n_targets <- sum(as.numeric(temp_data$target), na.rm = TRUE)
#         #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
#         
#         #Main subject df to wrangle, only one run now!
#         temp_data_clean <- temp_data %>% 
#             #get rid of trigger events
#             filter((!grepl('trigger', trial_type))) %>% 
#             #drop first event which is always flagged as a target
#             slice(-1) %>% 
#             mutate(target = recode(target, 'n/a' = '2')) %>% 
#             mutate(target = as.numeric(target)) 
#     
#             #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
#             pairs <- data.frame(first = head(temp_data_clean$target, -1), 
#                                 second = tail(temp_data_clean$target, -1))
#             temp_tab <- table(pairs)
# 
#             accu_percent <- (temp_tab[2,3]/n_targets)*100   
#             
#             #ADD METADATA to the temp df
#         
#             accu_temp <- data.frame(subject = bids_sub, group = groups[2],
#                                 
#                                 task = tasks[3], accu_percent = 
#                                     accu_percent)
#             
#         #Add this subject to group data
#         
#         df_VisualLoc_sighted_accu <- rbind(df_VisualLoc_sighted_accu, accu_temp)
#         
#         #clean up
# 
#     }
#           rm(temp_data, temp_data_clean, pairs, temp_tab,
#            sub_events, n_targets, bids_sub, accu_percent, i,j, accu_temp)
# }
#     
    

```


## SIGHTED VISUAL LOCALIZER: TW

```{r}
#Sighted subjects 
#sub-SC01 responded only to fix crosses, so was awake 
subject <- c('01','02','03','04', '05', '06', '07')


#Prepare df to store group accuracy
df_VisualLoc_sighted_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])
    
    #Grab events from this sub in this task 
    #Sub EB01 & EB02 doesn't have _run-01_ in sequence name...
    if(bids_sub == 'sub-SC01'){
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[3],
                                                  "_events\\.tsv$"), 
                                 recursive = TRUE)
    }else{
        sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                                 pattern = paste0(bids_sub,'_.*_' ,tasks[3],
                                                  "_run-01_events\\.tsv$"), 
                                 recursive = TRUE)}
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        #Sometimes first event is flagged as target, which is impossible. 
        # If that's the case, drop it from the number of targets
        if(as.numeric(temp_data$target[1]) == 1){
             n_targets <- sum(as.numeric(temp_data$target), na.rm = TRUE)-1
        } else {
            n_targets <- sum(as.numeric(temp_data$target), na.rm = TRUE)
        }
       
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #drop first event which is always flagged as a target
            slice(-1) %>% 
            #mutate(soundTarget = recode(soundTarget, 'n/a' = '2')) %>% 
            mutate(target = recode(target, 'n/a' = '2')) %>% 
            mutate(target = as.numeric(target)) 
        
        #Get pairs of subsequent events to look for a soundTARGET followed by RESPONSE
        #pairs <- data.frame(first = head(temp_data_clean$soundTarget, -1), 
         #                   second = tail(temp_data_clean$soundTarget, -1))
        #temp_tab <- table(pairs)
        
        
        ## NEW SOLUTION: HOW TO FIND THE RESPONSES WITHIN THE TW? 
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                   temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                  #  hit <- 0
                  #  temp_hits <- c(temp_hits, hit)
                #}
               
            } 
        }
        
        
        #accu_percent <- (temp_tab[2,3]/n_targets)*100 
        accu_percent <- (sum(temp_hits)/n_targets)*100
        
        #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                
                                task = tasks[3], accu_percent = 
                                    accu_percent)
        
        #Add this subject to group data
        df_VisualLoc_sighted_accu <- rbind(df_VisualLoc_sighted_accu, accu_temp)
        
        
    }
}
    
rm(tw_data, temp_data, accu_temp, temp_data_clean)  
    

```



## PLOTS
```{r}

#subject, group, task, accu_percent
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

plot_AudioLoc_accu <- blam_accuracy_points_sum(rbind(df_AudioLoc_blind_accu, df_AudioLoc_sighted_accu))

#still missing data from sub-SC04
plot_VisualLoc_accu <- blam_accuracy_points_sum_visloc(df_VisualLoc_sighted_accu)

```

