---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

1.  Auditory motion localizer
2.  Visual motion localizer
3.  Bimidal motion auditory
4.  Bimodal motion visual
5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)

```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
#tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
#           'task-bimodalMotionAud', 'task-bimodalMotionVis')

accu_tw <- 3
#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')
#env cleanup
rm(raw_repo)
```


## BLIND BIMODAL MOTION AUDIO

Issues to solve: 

- Which targets are the real targets? (only audio task!)

FOr sub-EB01 + 02 there are 3s and 2s
3 = static target (OF INTEREST!)
2 = motion target (OF INTEREST!)... but (see next point)

- How to approach target flagging where first stim from the pair is the target
(instead of the second), e.g. 
A 0 
B 0 
A 1 [target in logs]
A 0 [real target before the response]
Resp 2


THIS IS A SOLUTION TO CHANGE 2 -> 0 into 0 -> 2! 
IMPLEMENT IT!

^ 
This is irrelevant with the TIME WINDOW approach, you can just measure the TW from the first stimuli in pair :) 
```{r}
#Fix the 1-back encoding! 

#Get the original vector of targets 
# t_vec <- temp_data_clean$target
# 
# t_new <- c(0)
# 
# # Basically replace pairs of values in which 2 is proceeded by 0 
# # into pairs of 0 proceeded by 2, otherwise, keep the original value
# # (e.g. 3, 1 or n/a)
# 
# #Start with second row
# for (i in c(2:length(t_vec))) {
#     
#     #if this row is 0 and previous was 2
#     if (t_vec[i] == 0 & t_vec[i-1] == 2) {
#     
#         #Give it a new value of 2
#         t <- 2        
#         t_new <- c(t_new, t)
#     #if it was the original 2, switch it to 0 instead 
#     # [2, 0] -> [0, 2]
#     }else if(t_vec[i] == 2) {
#         
#         t_new <- c(t_new, 0)
#     #Otherwise, keep the original value from the log    
#     } else {
#         
#         t_new <- c(t_new, t_vec[i])
#     }
#     
#     
# }
# 
# #Add a new column to the original data frame
# df_new = data.frame(t_vec, t_new)
```


## BLIND: bimodalMotionAud - AVERAGE BETWEEN CONDITIONS
```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03', '05','06','07')
task <- 'bimodalMotionAud'

#Prepare df to store group accuracy
df_bimodMotAudio_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_bimodMotAudio_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        

        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
            # 3 = static target / 2 = motion target? but only for sub 01 & 02
            # rest have 2.000 as a general audio target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[1],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_bimodMotAudio_blind_run_accu <- rbind(df_bimodMotAudio_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotAudio_blind_summ_accu<- rbind(df_bimodMotAudio_blind_summ_accu, sub_accu_mean)
    
}
    
    

```

## BLIND: bimodalMotionAud - conditions (motion / static)
```{r}
subject <- c('01','02','03', '05','06','07')
task <- 'bimodalMotionAud'
conditions <- c('auditory_motion', 'auditory_static')


#Prepare df to store group accuracy
df_bimodMotAudio_blind_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        for(c in seq_along(conditions)){
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            #filter((!grepl('trigger', trial_type))) %>% 
             filter(trial_type == conditions[c] | trial_type == 'response') %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
            # 3 = static target / 2 = motion target? but only for sub 01 & 02
            # rest have 2.000 as a general audio target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                    '1.000000' = '1',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[1],
                                cond = conditions[c],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        
        
        
        }
        
        #Add data to accuracies by RUN
        #df_bimodMotAudio_blind_run_accu_cond <- rbind(df_bimodMotAudio_blind_run_accu_cond, sub_accu)
        
        
    }
    sub_accu_mean <- sub_accu %>% 
        group_by(cond) %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotAudio_blind_summ_accu_cond<- rbind(df_bimodMotAudio_blind_summ_accu_cond, sub_accu_mean)
}
 
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)     
```

## SIGHTED: bimodalMotionAud - AVERAGE BETWEEN CONDITIONS

```{r}
# This has to go by runs 
subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionAud'

#Prepare df to store group accuracy
df_bimodMotAudio_sighted_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_bimodMotAudio_sighted_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        

        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR SIGHTED:
            # 1 = visual fix target - ignore this due to EYES CLOSED
            # 2 = audio sound target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                   '1.000000' = '0',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[2],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_bimodMotAudio_sighted_run_accu <- rbind(df_bimodMotAudio_sighted_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotAudio_sighted_summ_accu<- rbind(df_bimodMotAudio_sighted_summ_accu, sub_accu_mean)
    
}
    
    

```

## SIGHTED: bimodalMotionAud - conditions (motion / static)
```{r}

subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionAud'
conditions <- c('auditory_motion', 'auditory_static')


#Prepare df to store group accuracy
df_bimodMotAudio_sighted_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        for(c in seq_along(conditions)){
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            #filter((!grepl('trigger', trial_type))) %>% 
             filter(trial_type == conditions[c] | trial_type == 'response') %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
            # 3 = static target / 2 = motion target? but only for sub 01 & 02
            # rest have 2.000 as a general audio target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                    '1.000000' = '0',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[2],
                                cond = conditions[c],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        
        
        
        }
        
        #Add data to accuracies by RUN
        #df_bimodMotAudio_blind_run_accu_cond <- rbind(df_bimodMotAudio_blind_run_accu_cond, sub_accu)
        
        
    }
    sub_accu_mean <- sub_accu %>% 
        group_by(cond) %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotAudio_sighted_summ_accu_cond<- rbind(df_bimodMotAudio_sighted_summ_accu_cond, sub_accu_mean)
}
 
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)   
```
 

## SIGHTED: bimodalMotionVis - AVERAGE BETWEEN CONDITIONS (motion/static)
DOES THIS EVEN MAKE SENSE? 
Does the script catch responses to OTHER TASK (target = 1, fix color change)
within the time window of response to target = 2?

```{r}
# This has to go by runs 
subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionVis'

#Prepare df to store group accuracy
df_bimodMotVis_sighted_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_bimodMotVis_sighted_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        

        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR SIGHTED:
            # 1 = visual fix target - ignore this due to EYES CLOSED
            # 2 = visual "motion" target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                   '1.000000' = '0',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[2],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_bimodMotVis_sighted_run_accu <- rbind(df_bimodMotVis_sighted_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotVis_sighted_summ_accu<- rbind(df_bimodMotVis_sighted_summ_accu, sub_accu_mean)
    
}
    
        #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)

```

## SIGHTED: bimodalMotionVis- conditions (motion / static)
```{r}

subject <- c('01','02','03', '04','07')
task <- 'bimodalMotionVis'
conditions <- c('visual_motion', 'visual_static')


#Prepare df to store group accuracy
df_bimodMotVis_sighted_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-' ,task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        for(c in seq_along(conditions)){
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            #filter((!grepl('trigger', trial_type))) %>% 
             filter(trial_type == conditions[c] | trial_type == 'response') %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: "ignore" 3s and 1s [fix cross colours]
            # 3 = static target / 2 = motion target? but only for sub 01 & 02
            # rest have 2.000 as a general audio target
            mutate(target = recode(target, '3' = '1', 
                                   '2' = '1',
                                   '2.000000' = '1',
                                   '1.000000' = '0',
                                   '1' = '0',
                                   'n/a' = '0')) 
        
        
        n_targets <- sum(as.numeric(temp_data_clean$target), na.rm = TRUE)
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$target[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
        

        
        accu_temp <- data.frame(subject = bids_sub, 
                                group = groups[2],
                                cond = conditions[c],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        
        
        
        }
        
        #Add data to accuracies by RUN
        #df_bimodMotAudio_blind_run_accu_cond <- rbind(df_bimodMotAudio_blind_run_accu_cond, sub_accu)
        
        
    }
    sub_accu_mean <- sub_accu %>% 
        group_by(cond) %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotVis_sighted_summ_accu_cond<- rbind(df_bimodMotVis_sighted_summ_accu_cond, sub_accu_mean)
}
 
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)   
```
 


clean up
```{r}
rm(pairs, accu_temp, sub_accu, sub_accu_mean, temp_data, temp_data_clean)
```

## ----- PLOTS -----


```{r}
#Group SUM
#source plotting functions
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

df_AudioV1_summ_plot <- rbind(df_AudioV1_blind_summ_accu,
                                              df_AudioV1_sighted_summ_accu) %>% 
    mutate(accu_percent = mean_accu)

plot_AudioV1_accu <- blam_accuracy_points_sum(df_AudioV1_summ_plot)

#facet by subjects to show runs

plot_Audio_V1_accu_run_blind <- blam_accuracy_points_run(df_AudioV1_blind_run_accu)

plot_Audio_V1_accu_run_sighted <- blam_accuracy_points_run(df_AudioV1_sighted_run_accu)
#plot_Audio_V1_accu_run_sighted
```


Plots for each condition
```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))


dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

lables <- c('Motion (A)', 'Static (A)')



# BY GROUP 
df_bimodMotAudio_cond_BLIND_plot <- df_bimodMotAudio_blind_summ_accu_cond %>% 
    mutate(cond = factor(cond, levels = c('auditory_motion', 'auditory_static'))) %>% 
    mutate(accu_percent = mean_accu)

df_bimodMotAudio_cond_SIGHTED_plot <- df_bimodMotAudio_sighted_summ_accu_cond %>% 
    mutate(cond = factor(cond, levels = c('auditory_motion', 'auditory_static'))) %>% 
    mutate(accu_percent = mean_accu)

df_bimodMotVis_cond_SIGHTED_plot <- df_bimodMotVis_sighted_summ_accu_cond %>% 
    mutate(cond = factor(cond, levels = c('visual_motion', 'visual_static'))) %>% 
    mutate(accu_percent = mean_accu)



plot_blind <- blam_accuracy_points_sum_conditions_group(df_bimodMotAudio_cond_BLIND_plot, lables, dark_colors[1])

plot_sighted_audio <- blam_accuracy_points_sum_conditions_group(df_bimodMotAudio_cond_SIGHTED_plot, lables, dark_colors[2])


labels_vis <- c('Motion (V)', 'Static (V)')
plot_sighted_vis <- blam_accuracy_points_sum_conditions_group(df_bimodMotVis_cond_SIGHTED_plot, 
                                                                labels_vis, 
                                                                dark_colors[2])

```



----- TEST REWRITE LOGS ----- 

```{r}
#Fix the 1-back encoding! 

#Get the original vector of targets 
t_vec <- temp_data_clean$target

t_new <- c(0)

# Basically replace pairs of values in which 2 is proceeded by 0 
# into pairs of 0 proceeded by 2, otherwise, keep the original value
# (e.g. 3, 1 or n/a)

#Start with second row
for (i in c(2:length(t_vec))) {
    
    #if this row is 0 and previous was 2
    if (t_vec[i] == 0 & t_vec[i-1] == 2) {
    
        #Give it a new value of 2
        t <- 2        
        t_new <- c(t_new, t)
    #if it was the original 2, switch it to 0 instead 
    # [2, 0] -> [0, 2]
    }else if(t_vec[i] == 2) {
        
        t_new <- c(t_new, 0)
    #Otherwise, keep the original value from the log    
    } else {
        
        t_new <- c(t_new, t_vec[i])
    }
    
    
}

#Add a new column to the original data frame
df_new = data.frame(t_vec, t_new)
```


```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01')


#Prepare df to store group accuracy
df_bimodMotAudio_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_bimodMotAudio_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[4], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE) %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type)))
        

        ## RE-WRITE THE 1-BACK TARGET VALUES FOR THE AUDITORY TASK! 
        t_vec <- temp_data$target
        target_fixed <- c(0)

        # Basically replace pairs of values in which 2 is proceeded by 0 
        # into pairs of 0 proceeded by 2, otherwise, keep the original value
        # (e.g. 3, 1 or n/a)
        
        #Start with second row
        for (i in c(2:length(t_vec))) {
            
            #if this row is 0 and previous was 2
            if (t_vec[i] == 0 & t_vec[i-1] == 2) {
            
                #Give it a new value of 2
                t <- 2        
                target_fixed <- c(target_fixed, t)
            #if it was the original 2, switch it to 0 instead 
            # [2, 0] -> [0, 2]
            }else if(t_vec[i] == 2) {
                
                target_fixed <- c(target_fixed, 0)
            #Otherwise, keep the original value from the log    
            } else {
                
                target_fixed <- c(target_fixed, t_vec[i])
            }
            
            
        }
        
        temp_data <- data.frame(temp_data, target_fixed)
        
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data  %>% 
            #mutate(target = as.numeric(target)) %>% 
            #REASSIGN TARGET VALUES: FOR BLIND: 3 = static target, 2 = motion target
           mutate(target_fixed = recode(target_fixed, '3' = '1', 
                                   '2' = '1',
                                   '1' = '0',
                                   'n/a' = '2')) %>% 
            mutate(target_fixed = as.numeric(target_fixed))
            
            
        ## WHY IS THERE AN ERROR HERE?
            pairs <- data.frame(first = head(temp_data_clean$target_fixed, -1), 
                                second = tail(temp_data_clean$target_fixed, -1))
            temp_tab <- table(pairs)
 
            n_targets <- sum(as.numeric(temp_data$target_fixed), na.rm = TRUE)

        accu_percent <- (temp_tab[2,3]/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = tasks[4], accu_percent = 
                                    accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_bimodMotAudio_blind_run_accu <- rbind(df_bimodMotAudio_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_bimodMotAudio_blind_summ_accu<- rbind(df_bimodMotAudio_blind_summ_accu, sub_accu_mean)
    
}
    
    

```
