---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

1.  Auditory motion localizer
2.  Visual motion localizer
3.  Bimidal motion auditory
4.  Bimodal motion visual
5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho) #For d'
library(RColorBrewer)
library(cowplot)

```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
#tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
#           'task-bimodalMotionAud', 'task-bimodalMotionVis')
task <- 'audioV1'
#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')

accu_tw <- 3
#env cleanup
rm(raw_repo)
```


## BLIND AUDIO V1: average performance

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03','04', '05','07')


#Prepare df to store group accuracy
df_AudioV1_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        
        # TRY TO ADD ANOTHER LOOP WITH CONDITIONS?
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
        
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$oneBack[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_AudioV1_blind_run_accu <- rbind(df_AudioV1_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_blind_summ_accu<- rbind(df_AudioV1_blind_summ_accu, sub_accu_mean)
 
    
     #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)     
}
    
    

```



## BLIND AUDIO V1 (conditions test)

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03','04', '05','07')
conditions <- c('object','voice','scrambled_object','scrambled_voice')

#Prepare df to store group accuracy
df_AudioV1_blind_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_blind_run_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        
        for(c in seq_along(conditions)){
            
            
            #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
            
            
            #Main subject df to wrangle, only one run now!
            
            # Create a clean dataframe: only selected condition + response
            temp_data_clean <- temp_data %>% 
                #get rid of trigger events
                filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                # filter((!grepl('trigger', trial_type))) %>% 
                mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
                mutate(oneBack = as.numeric(oneBack)) 
            
            #Check the number of targets for %Accuracy
            n_targets <- sum(as.numeric(temp_data_clean$oneBack), na.rm = TRUE)
            
            temp_hits <- c()
            
            for(iRow in 1:nrow(temp_data_clean)){
                
                #If this trial is a target
                if(temp_data_clean$oneBack[iRow]== 1){
                    
                    #Note the target onset
                    tar_onset <- temp_data_clean$onset[iRow]
                    
                    #Slice the DF based on the TW? 
                    tw_data <- temp_data_clean %>% 
                        filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                    
                    
                    #Check if there is a response within that time window
                    if(Reduce("|", tw_data$trial_type=='response')){
                        
                        hit <- 1
                        temp_hits <- c(temp_hits, hit)
                        #temp_hits[iRow] <- 1
                    } #else {
                    #  hit <- 0
                    #  temp_hits <- c(temp_hits, hit)
                    #}
                    
                } 
            }
            
            
            accu_percent <- (sum(temp_hits)/n_targets)*100
            
            #ADD METADATA to the temp df
            
            accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                    cond = conditions[c],
                                    run_num = j,
                                    run_lab = paste0('run-0',j),
                                    task = task, 
                                    accu_percent = accu_percent)
            #Add this run to subject data
            sub_accu <- rbind(sub_accu, accu_temp)
            
            
            
        }
        
        #Add data to accuracies by RUN
        df_AudioV1_blind_run_accu_cond <- rbind(df_AudioV1_blind_run_accu_cond, sub_accu)
        
    }
    
     sub_accu_mean <- sub_accu %>% 
         group_by(cond) %>% 
         mutate(mean_accu = mean(accu_percent)) %>% 
         dplyr::select(-c(run_lab, run_num,cond, accu_percent)) %>% 
         slice(1)
     
    # #Add data to accuracy summaries by subject
    df_AudioV1_blind_summ_accu_cond<- rbind(df_AudioV1_blind_summ_accu_cond, sub_accu_mean)
    
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)  
}

  

```

## SIGHTED AUDIO V1

```{r}
#List of subjects for this particular task

# This has to go by runs 
subject <- c('01','02','03','04', '05','06','07')


#Prepare df to store group accuracy
df_AudioV1_sighted_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_sighted_run_accu <- data.frame(stringsAsFactors = FALSE)

for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
        
        
        temp_hits <- c()
        
        for(iRow in 1:nrow(temp_data_clean)){
            
            #If this trial is a target
            if(temp_data_clean$oneBack[iRow]== 1){
                
                #Note the target onset
                tar_onset <- temp_data_clean$onset[iRow]
                
                #Slice the DF based on the TW? 
                tw_data <- temp_data_clean %>% 
                    filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                
                
                #Check if there is a response within that time window
                if(Reduce("|", tw_data$trial_type=='response')){
                    
                    hit <- 1
                    temp_hits <- c(temp_hits, hit)
                    #temp_hits[iRow] <- 1
                } #else {
                #  hit <- 0
                #  temp_hits <- c(temp_hits, hit)
                #}
                
            } 
        }
        

        accu_percent <- (sum(temp_hits)/n_targets)*100
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = task, 
                                accu_percent = accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_AudioV1_sighted_run_accu <- rbind(df_AudioV1_sighted_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_sighted_summ_accu<- rbind(df_AudioV1_sighted_summ_accu, sub_accu_mean)
    
    
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)  
}
    

```

SIGHTED AUDIO V1: CONDITIONS
```{r}

subject <- c('01','02','03','04', '05','06','07')
conditions <- c('object','voice','scrambled_object','scrambled_voice')

#Prepare df to store group accuracy
df_AudioV1_sighted_summ_accu_cond <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_sighted_run_accu_cond <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_task-',task, ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
        
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                    sep = '/'), header=TRUE)
        
        
        for(c in seq_along(conditions)){
            
            
            #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
            
            
            #Main subject df to wrangle, only one run now!
            
            # Create a clean dataframe: only selected condition + response
            temp_data_clean <- temp_data %>% 
                #get rid of trigger events
                filter(trial_type == conditions[c] | trial_type == 'response') %>% 
                # filter((!grepl('trigger', trial_type))) %>% 
                mutate(oneBack = recode(oneBack, 'n/a' = '0')) %>% 
                mutate(oneBack = as.numeric(oneBack)) 
            
            #Check the number of targets for %Accuracy
            n_targets <- sum(as.numeric(temp_data_clean$oneBack), na.rm = TRUE)
            
            temp_hits <- c()
            
            for(iRow in 1:nrow(temp_data_clean)){
                
                #If this trial is a target
                if(temp_data_clean$oneBack[iRow]== 1){
                    
                    #Note the target onset
                    tar_onset <- temp_data_clean$onset[iRow]
                    
                    #Slice the DF based on the TW? 
                    tw_data <- temp_data_clean %>% 
                        filter(onset <= tar_onset + accu_tw & onset > tar_onset-1)
                    
                    
                    #Check if there is a response within that time window
                    if(Reduce("|", tw_data$trial_type=='response')){
                        
                        hit <- 1
                        temp_hits <- c(temp_hits, hit)
                        #temp_hits[iRow] <- 1
                    } #else {
                    #  hit <- 0
                    #  temp_hits <- c(temp_hits, hit)
                    #}
                    
                } 
            }
            
            
            accu_percent <- (sum(temp_hits)/n_targets)*100
            
            #ADD METADATA to the temp df
            
            accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                    cond = conditions[c],
                                    run_num = j,
                                    run_lab = paste0('run-0',j),
                                    task = task, 
                                    accu_percent = accu_percent)
            #Add this run to subject data
            sub_accu <- rbind(sub_accu, accu_temp)
            
            
            
        }
        
        #Add data to accuracies by RUN
        df_AudioV1_sighted_run_accu_cond <- rbind(df_AudioV1_sighted_run_accu_cond, sub_accu)
        
    }
    
     sub_accu_mean <- sub_accu %>% 
         group_by(cond) %>% 
         mutate(mean_accu = mean(accu_percent)) %>% 
         dplyr::select(-c(run_lab, run_num,cond, accu_percent)) %>% 
         slice(1)
     
    # #Add data to accuracy summaries by subject
    df_AudioV1_sighted_summ_accu_cond<- rbind(df_AudioV1_sighted_summ_accu_cond, sub_accu_mean)
    
    #Small cleanup
    rm(accu_temp,sub_accu, sub_accu_mean, tw_data, temp_data, temp_data_clean)  
}

  

```

## ----- PLOTS -----

Average Plots (across conditions)
```{r}
#Group SUM
#source plotting functions
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

df_AudioV1_summ_plot <- rbind(df_AudioV1_blind_summ_accu,
                              df_AudioV1_sighted_summ_accu) %>% 
    mutate(accu_percent = mean_accu)

plot_AudioV1_accu <- blam_accuracy_points_sum(df_AudioV1_summ_plot)

#facet by subjects to show runs
plot_Audio_V1_accu_run_blind <- blam_accuracy_points_run(df_AudioV1_blind_run_accu)

plot_Audio_V1_accu_run_sighted <- blam_accuracy_points_run(df_AudioV1_sighted_run_accu)
#plot_Audio_V1_accu_run_sighted
```

Plots for each condition
```{r}
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))


dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 

lables <- c('O', 'V', 'ScO', 'ScV')

#Rename variable in DF? 
df_AudioV1_cond_plot <- rbind(df_AudioV1_blind_summ_accu_cond,
                              df_AudioV1_sighted_summ_accu_cond) %>% 
    mutate(cond = factor(cond, levels = c('object', 'voice', 'scrambled_object', 'scrambled_voice'))) %>% 
    mutate(accu_percent = mean_accu)


plot_AudioV1_cond_test <- blam_accuracy_points_sum_conditions(df_AudioV1_cond_plot)
plot_AudioV1_cond_test


# BY GROUP 
df_AudioV1_cond_BLIND_plot <- df_AudioV1_blind_summ_accu_cond %>% 
    mutate(cond = factor(cond, levels = c('object', 'voice', 'scrambled_object', 'scrambled_voice'))) %>% 
    mutate(accu_percent = mean_accu) %>% 
    filter(subject != 'sub-EB02')

df_AudioV1_cond_SIGHTED_plot <- df_AudioV1_sighted_summ_accu_cond %>% 
    mutate(cond = factor(cond, levels = c('object', 'voice', 'scrambled_object', 'scrambled_voice'))) %>% 
    mutate(accu_percent = mean_accu)



plot_blind <- blam_accuracy_points_sum_conditions_group(df_AudioV1_cond_BLIND_plot, lables, dark_colors[1])

plot_sighted <- blam_accuracy_points_sum_conditions_group(df_AudioV1_cond_SIGHTED_plot, lables, dark_colors[2])
```

