---
title: "BLAM_Liege_beh_analyses"
author: "Jacek Matuszewski"
date: '2023-09-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic info about projects and tasks

BLAM project includes following sub-projects (and their behavioural conditions and tasks)

WATCHOUT: sighted subjects perform TWO tasks in motion, one audio and one visual so some responses my be to FixationTargets and some to AuditoryTargets

1.  Auditory motion localizer
2.  Visual motion localizer
3.  Bimidal motion auditory
4.  Bimodal motion visual
5.  Audio V1

Not all groups have all tasks!

This script loads and wrangles data for each task and subject and summarizes them in a group data frame and makes basic plots

Load packages

```{r load packages, echo = FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(stringi)
library(rstatix)
#library(psycho)
library(RColorBrewer)
library(cowplot)

```

## Define basic variables

```{r}
#Setup some paths
project_path <- '/Volumes/Slim_Reaper/Projects/BLAM_Liege_project/Behavioural_data_all' #main yoda folder for this script
raw_repo <- '2023_Liege_BLAM_MB_raw'
inputs <- paste(project_path, 'inputs', raw_repo, sep = '/') #datalad raw repo in inputs
deriv_r <- paste(project_path, 'outputs','derivatives', 'R_beh_data', sep = '/') #basic output for this script


#base names for tasks to be BIDSified in loops later on
tasks <- c('task-audioV1', 'task-auditoryLocalizer', 'task-visualLocalizer', 
           'task-bimodalMotionAud', 'task-bimodalMotionVis')

#prefixes for groups, Early Blind (EB) and Sighted Controls (SC)
groups <- c('EB', 'SC')
#env cleanup
rm(raw_repo)
```


## BLIND AUDIO V1

```{r}
#List of subjects for this particular task
# still waiting for others to be pushed to RAW REPO

# This has to go by runs 
subject <- c('01','02','03','04', '05','07')


#Prepare df to store group accuracy
df_AudioV1_blind_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_blind_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[1],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[1], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
        #n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '2')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
            
            
            pairs <- data.frame(first = head(temp_data_clean$oneBack, -1), 
                                second = tail(temp_data_clean$oneBack, -1))
            temp_tab <- table(pairs)
 
            
        accu_percent <- (temp_tab[2,3]/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[1],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = tasks[1], accu_percent = 
                                    accu_percent)
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        


    }
    
    #Add data to accuracies by RUN
    df_AudioV1_blind_run_accu <- rbind(df_AudioV1_blind_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_blind_summ_accu<- rbind(df_AudioV1_blind_summ_accu, sub_accu_mean)
    
}
    
    

```

## SIGHTED AUDIO V1

```{r}
#List of subjects for this particular task

# This has to go by runs 
subject <- c('01','02','03','04', '05','06','07')


#Prepare df to store group accuracy
df_AudioV1_sighted_summ_accu <- data.frame(stringsAsFactors = FALSE)
df_AudioV1_sighted_run_accu <- data.frame(stringsAsFactors = FALSE)

#Loop across subjects 
for(i in seq_along(subject)) {
    
    bids_sub <- paste0('sub-',groups[2],subject[i])

    #Grab events from this sub in this task 
    sub_events <- list.files(path = paste(inputs,bids_sub, sep = '/'),
                     pattern = paste0(bids_sub,'_.*_' ,tasks[1], ".*_events\\.tsv$"), 
                     recursive = TRUE)
    
    sub_accu <- data.frame(stringsAsFactors = FALSE)
    
    for(j in seq_along(sub_events)){
          
        temp_data<-read.table(paste(inputs, bids_sub, sub_events[j],
                                sep = '/'), header=TRUE)
        
        n_targets <- sum(as.numeric(temp_data$oneBack), na.rm = TRUE)
       # n_responses <- temp_data %>% filter(trial_type == "response") %>% nrow()
        
        #Main subject df to wrangle, only one run now!
        temp_data_clean <- temp_data %>% 
            #get rid of trigger events
            filter((!grepl('trigger', trial_type))) %>% 
            mutate(oneBack = recode(oneBack, 'n/a' = '2')) %>% 
            mutate(oneBack = as.numeric(oneBack)) 
            
            
            pairs <- data.frame(first = head(temp_data_clean$oneBack, -1), 
                                second = tail(temp_data_clean$oneBack, -1))
            temp_tab <- table(pairs)
            
        accu_percent <- (temp_tab[2,3]/n_targets)*100   
            
            #ADD METADATA to the temp df
        
        accu_temp <- data.frame(subject = bids_sub, group = groups[2],
                                run_num = j,
                                run_lab = paste0('run-0',j),
                                task = tasks[1], accu_percent = 
                                    accu_percent)
        
        #Add this run to subject data
        sub_accu <- rbind(sub_accu, accu_temp)
        
        

    }
 
    df_AudioV1_sighted_run_accu <- rbind(df_AudioV1_sighted_run_accu, sub_accu)
    
    sub_accu_mean <- sub_accu %>% 
        mutate(mean_accu = mean(accu_percent)) %>% 
        dplyr::select(-c(run_lab, run_num,accu_percent)) %>% 
        slice(1)
    
    #Add data to accuracy summaries by subject
    df_AudioV1_sighted_summ_accu<- rbind(df_AudioV1_sighted_summ_accu, sub_accu_mean)
    
    
      #  rm(temp_data, temp_data_clean, pairs, temp_tab, hit,
      #    sub_events, n_responses, n_targets, bids_sub, accu_percent, i,j,
      #    sub_accu, sub_accu_mean, accu_temp)
}
    
    

```


clean up
```{r}
rm(pairs, accu_temp, sub_accu, sub_accu_mean, temp_data, temp_data_clean)
```

## ----- PLOTS -----


```{r}
#Group SUM
#source plotting functions
source(paste(project_path,'code','src','BLAM_functions_plots.R', sep = '/'))

df_AudioV1_summ_plot <- rbind(df_AudioV1_blind_summ_accu,
                                              df_AudioV1_sighted_summ_accu) %>% 
    mutate(accu_percent = mean_accu)

plot_AudioV1_accu <- blam_accuracy_points_sum(df_AudioV1_summ_plot)

#facet by subjects to show runs

plot_Audio_V1_accu_run_blind <- blam_accuracy_points_run(df_AudioV1_blind_run_accu)

plot_Audio_V1_accu_run_sighted <- blam_accuracy_points_run(df_AudioV1_sighted_run_accu)
#plot_Audio_V1_accu_run_sighted
```
